---
title: "simpleRegress"
author: "Melanyy vasquez"
date: "Summer 2021"
output: html_document
---

```{r setup, include=FALSE}
knitr::opts_chunk$set(echo = TRUE)
```

## make a simple regression model

```{r}
bears <- read.csv(file="BEARS.csv",header = TRUE)
```

## Model LENGTH ~ NECK  this is an example  

```{r}
simp <- lm(LENGTH~NECK,data=bears)
plot(LENGTH~NECK,data=bears)
abline(simp)
summary.lm(simp)
```

## now predict the length of a bear who has a neck of 17, 22 and 26


```{r}
new <- data.frame(NECK=c(17,22,26))
predict(simp,new)
predict(simp,new,se.fit=TRUE)
```
## Surely there is another variable that can better predict LENGTH than NECK. Find one and compare its performance to that of neck by it value of Adjusted-Rsquared (bigger is better).

I will try to find a model of length of a bear based on chest. 


```{r}
mychest <- lm(LENGTH~CHEST,data=bears)
plot(LENGTH~CHEST,data=bears)
abline(mychest)
summary.lm(mychest)
```

This LENGTH~CHEST model shows the adjusted R square here is 0.7869, and is slight bigger number than LENGTH~NECK model; The residual standard error is 4.939 which is a smaller number than LENGTH~NECK model as well.

In the LENGTH~NECK model the adjusted R square was 0.747 and the residual standard error number was 5.376. 

The best model used is the LENGTH~CHEST model because it explains more of the errors made , and its residual standard error is smaller.



```{r}
myheadw <- lm(LENGTH~HEADWTH,data=bears)
plot(LENGTH~HEADWTH,data=bears)
abline(myheadw)
summary.lm(myheadw)
```

This LENGTH~HEADWTH model,isn't as useful. 
The adjusted R square is 0.532 and has gone downwards and residual standard error has gone up to 7.32 and displaying immediate failure results.







